Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-05 Manuscript.Rmd
Updated the references to a format that will read .bib files

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  pdf_document: default
  html_document: default
  word_document: 
    reference_docx: Style_reference.docx
bibliography: mPFC_paper.bib
---

@@

  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016). More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018). While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018). Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018). In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018). A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018). From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data (BLAH.) This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2016). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study.

@@

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. (2011). We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

@@

In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements (Tobyne et al., 2017). These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression (MGSR; Burgess et al., 2016). Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

To establish each subject's network, we selected all the vertices contained within the ROIs (n = **5,564 (UPDATE)** per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of the correlations so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately; 2) the concatenated timeseries from each pair of daily sessions; 3) each subject's dataset; and 4) on each step of a sliding window analysis (see Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975). First, each adjusted network was represented as an n x n correlation matrix (where n = number of vertices within the ROIs, 5,564). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $W$ is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization (using the algorithm from Clauset et al., XXXX). This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can fractionate a network into many functional groups. If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

@@

In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (RI; Rand, 2012) as the reference metric of agreement between two clusterings. The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g. clustered together on A, but separately on B). The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme. *(SHOULD WE INCLUDE THIS? The mutual information results would probably need to go in the supplemental materials) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).*

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (ADD TO CODE). We then estimate the level of agreement between scans taken across days (i.e. pairs of daily left-right and right-left phase encoding sessions). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject. We then extend this idea by computing the overall agreement across all sessions. Similarly, we expect that sessions within subject will show higher agreement than between subjects. Finally, we perform a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37) 8) comparing each window's functional pattern against the clustering derived from the whole subject's data. This approach should give us a sense of the dynamics of the functional organization of mPFC during rest. We complement this analysis by calculating the proportion of times each surface vertex was affiliated with the DMN community across time, as well as computing the flexibility of each node (i.e. the number of times each vertex changed affiliation across time). Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013], we also performed these comparisons for PCC and mPFC separately. Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects. On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject. We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects. Ratios close to one denote good alignment across subjects, while ratios significantly higher than one suggest that partitions per subject were more stable than what you would expect against every other subject.

@@

A potential downfall of the present approach is that it can be computationally demanding, while more direct seed-based functional connectivity methods could provide sufficient approximations of an individual's DMN orgnization. We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation. For each subject's concatenated day 1 and day 2 scans, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs. The resulting day 1 and day 2 mPFC maps were then correlated within and between subjects in three ways: 1) between correlation-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps. These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement. These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018] [-@Mueller2013]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features. To do this, we correlated each subject's Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex). These simple correlations are aimed to provide a sense of this possible relationship, which can be studied in depth in the future.

@@

We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures (see Methods). Using each literature's mean number of reports per area as the null probability (DMN = ; SV = ), one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.

Figure 1 shows the resulting ROIs from these analyses. As expected, overlapping areas included 15 bilateral regions in PCC (**Probably need to add their respective stats here** 31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi). Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).

@@

First, we estimated each individual's DMN coverage using the whole time series (4800 TRs). On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r sddAll`). Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.

@@

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
  pdf_document: default
bibliography: mPFC_paper.bib
---

@@

  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. However, the distributed cortical valuation system also includes posterior cingulate (PCC) and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011]. This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009]. Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016]. More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017]. These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018]. While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018]. Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2016]. In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017]. It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis]. As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016]. We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2010] (n = 27 studies) and DMN [@Laird2009] (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016]. This produced a list of standardized parcels that were reported on each study.

@@

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. [-@Yeo2011]. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

@@

In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

Beyond the in-house minimally preprocessed pipeline from HCP [@Glasser2013], which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements [@Tobyne2017]. These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression [@Burgess2016]. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,319 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of the correlations so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2018]. First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,319). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $W$ is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization using the algorithm from Clauset et al. [-@Clauset2004]. This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can fractionate a network into many functional groups. If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

@@

In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) [@Hubert1985] as the reference metric of agreement between two clusterings. The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g. clustered together on A, but separately on B). The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme. *(SHOULD WE INCLUDE THIS? The mutual information results would probably need to go in the supplemental materials) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).*

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (**ADD TO CODE**). We then estimate the level of agreement between scans taken across days (i.e. pairs of daily left-right and right-left phase encoding sessions). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject. We then extend this idea by computing the overall agreement across all sessions. Similarly, we expect that sessions within subject will show higher agreement than between subjects. Finally, we perform a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37) 8) comparing each window's functional pattern against the clustering derived from the whole subject's data. This approach should give us a sense of the dynamics of the functional organization of mPFC during rest. We complement this analysis by calculating the proportion of times each surface vertex was affiliated with the DMN community across time, as well as computing the flexibility of each node (i.e. the number of times each vertex changed affiliation across time). Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013], we also performed these comparisons for PCC and mPFC separately. Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects. On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject. We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects. Ratios close to one denote good alignment across subjects, while ratios significantly higher than one suggest that partitions per subject were more stable than what you would expect against every other subject.

@@

A potential downfall of the present approach is that it can be computationally demanding, while more direct seed-based functional connectivity methods could provide sufficient approximations of an individual's DMN orgnization. We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation. For each subject's concatenated day 1 and day 2 scans, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs. The resulting day 1 and day 2 mPFC maps were then correlated within and between subjects in three ways: 1) between correlation-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps. These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement. These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018; -@Mueller2013]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features. To do this, we correlated each subject's Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex). These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.

@@

``` {r ROI computation, echo=FALSE, message = FALSE}
  ## ROI definition
  # First, load the raw count csv files
  valCounts <- read.csv2('decCounts.csv', sep = ",")
  dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

  # Then, get the means of the counts per domain
  tempBoot <- bootstrap(valCounts$Counts)
  BV <- round(mean(tempBoot))
  BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
  tempBoot <- bootstrap(dmnCounts$Counts)
  BD <- round(mean(tempBoot))
  BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
  rm(tempBoot)

  # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
  # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
  for (i in seq(valCounts$Counts)) {
    indx <- valCounts$Counts[i]
    tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
    valCounts$Chi[i] <- tempTest$statistic
    valCounts$pVal[i] <- tempTest$p.value
  }

  for (i in seq(dmnCounts$Counts)) {
    indx <- dmnCounts$Counts[i]
    tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
    dmnCounts$Chi[i] <- tempTest$statistic
    dmnCounts$pVal[i] <- tempTest$p.value
  }

  # This part is just for reference, as the labels are loaded from a file
  # # Retain only the significant parcels
  # t1 <- valCounts$Label[valCounts$pVal < 0.05]
  # t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
  # 
  # # Remove hemispheric references 
  # t1 <- unique(substring(t1,2))
  # t2 <- unique(substring(t2,2))
  # 
  # # And get the set of overlapping areas between literatures
  # # This is missing some cingulate and PFC areas, and adds V2.
  # # However, we can say that we are filling in the gap for completeness,
  # # and removing V2 because it's demonstrably irrelevant.
  # bothLbls_alt <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
  # 
  # # You could also try to permute the allocation of reports per literature,
  # # and then perform a chi-squared per parcel. Get the max stat per iteration.
  # # Now you have your null distribution.
```

We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions across DMN and SV literatures (see Methods). Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.

Figure 1 shows the resulting ROIs from these analyses. As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).

@@

With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 TRs). Each subject's network was constructed by performing pairwise correlations among the time series of all the vertices contained within the ROIs. After correcting for multiple tests, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r sddAll`). This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016]. Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.

@@

Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.

## Acknowledgements
Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
